Contextual Combinatorial Cascading Bandits

### 2015-11-20 contextual combinatorial cascading bandits.tex
complete proof for the 'and' case with discount

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{X_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s): k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. By equation (\ref{eq:expectation}), we have $\EE[(\gamma_k\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k X_{s,\ba_k^s})$. By ridge regression of data 
$$
\{(\gamma_k X_{s,\ba_k^s}, \gamma_k\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]}
$$
	let $\hat{\theta}_t$ be the $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
	\begin{equation}
	\hat{\theta}_t = (X^{t,\top}X^{t} + \lambda I)^{-1} X^{t, \top} \bY^t
	\end{equation}
	where $X^t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k X_{s,\ba_k^s}^{\top}$ and $\bY^t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
	$$
	\bV_t = X^{t,\top}X^{t} + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma^{2k-2}X_{s,\ba_k^s}X_{s,\ba_k^s}^{\top}.
	$$
	Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.
	\subsection{Algorithm}

@@

\section{Analysis}
Let
\begin{equation}
	C_\gamma = \sum_{k=1}^{K} \gamma_k^2.
\end{equation}

@@

	\begin{lemma}
		\label{lem:estimateTech}
		Let $0 \leq p_1,...,p_K \leq 1$ and $u_1,...,u_K \geq 0$. Then
		\begin{align*}
		&~~\sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\} \\
		& \leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^K \gamma_k u_k.
		\end{align*}
	\end{lemma}
	\begin{proof}
		We prove this by induction. It holds obviously for $K=1$.
		\begin{align*}
		&~~\sum_{k=1}^{K+1} \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\} \\
		&\leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\}\\
		&+\gamma_{K+1}\prod_{i=1}^{K}(1-\min\{p_i+u_i, 1\})\min\{p_{K+1}+u_{K+1}, 1\}\\
		&\leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^K \gamma_k u_k\\
		&+\gamma_{K+1}\prod_{i=1}^{K}(1-p_i)(p_{K+1}+u_{K+1})\\
		&\leq \sum_{k=1}^{K+1} \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^{K+1} \gamma_k u_k
		\end{align*}
	\end{proof}

@@

\begin{lemma}

\end{lemma}

\begin{proposition}
	With high probability $1-\delta$, $E[\Delta_{\bA_t}|\cH_t] \leq \frac{2}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$
\end{proposition}
\begin{proof}
	Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t)$, then
	\begin{align*}
		&\sum_{k=1}^{\abs{A_t^*}}\gamma_k (\prod_{i=1}^{k-1}(1 -\bU_t(a_{t,i}^*)))\bU_t(a_{t,k}^*) \\
		\leq &\sum_{k=1}^{\abs{\bA_t}}\gamma_k (\prod_{i=1}^{k-1}(1 -\bU_t(\ba_i^t)))\bU_t(\ba_k^t) 
	\end{align*}
		By lemma \ref{lem:estimateU} and lemma \ref{lem:increasing}, it holds that
		\begin{align*}
		&~~f(A_t^*, \theta_*^{\top}X_t) \\
		&\leq f(\bA_t, \min\{\theta_*^{\top}X_{t,a}+2\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}},1\}).
		\end{align*}
		Therefore by lemma \ref{lem:estimateTech},
		\begin{align*}
		&~~f(A_t^*, \theta_*^{\top}X_t) \\
		&\leq  \sum_{k=1}^{\abs{\bA_t}}\gamma_k (\prod_{i=1}^{k-1}(1 -\theta_*^{\top}X_{t,a_{t,i}^*})\theta_*^{\top}X_{t,a_{t,k}^*} \\
		&~~ + 2\sum_{k=1}^{\abs{\bA_t}}\gamma_k\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}\\
		&=f(\bA_t, \theta_*^{\top}X_t) + 2\beta_{t-1}(\delta)\sum_{k=1}^{\abs{\bA_t}}\gamma_k\norm{X_{t,a}}_{\bV_{t-1}^{-1}},
		\end{align*}
		which is equivalent to 
		$$
		\Delta_{\bA_t} \leq 2\sum_{k=1}^{\abs{\bA_t}}\gamma_k\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
		$$
	\end{proof}

	\begin{theorem}
		For any $\delta > 0$, with probability at least $1 - \delta$, we have
		\begin{equation}
		R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT})
		\end{equation}
	\end{theorem}
	\begin{proof}
		With probability at least $1-\delta$,
		\begin{equation}
		\begin{split}
		&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{\bA_t}] \\
		&\leq \sum_{t=1}^{T} \frac{8}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\\
		&\leq \frac{8}{f^*}\beta_T(\delta) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
		&\leq \frac{8}{f^*}\beta_T(\delta) \sqrt{(\sum_{t=1}^T\bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\gamma^{2k-2}\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}\\
		&\leq O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{TK})
		\end{split}
		\end{equation}
	\end{proof}

\begin{lemma} % det(V_t)
	$\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
\end{lemma}
\begin{proof}
	We have $\det(\bV_t) \leq (\trace(\bV_t)/d)^d$ and
	\begin{align*}
	\trace(\bV_t) &= \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma^{2k-2} \trace(X_{s,\ba_k^s} X_{s,\ba_k^s}^{\top})\\
	& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma^{2k-2} \norm{X_{s,\ba_k^s}}_2^2\\
	& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma^{2k-2}=d\lambda + tC_\gamma.
	\end{align*}
\end{proof}

\begin{lemma} % technical lemma for det
	Let $x_i \in \RR^{d \times 1}, 1 \leq i \leq n$. Then we have
	$$
	\det(I + \sum_{i=1}^n x_i x_i^{\top}) \geq 1 + \sum_{i=1}^n \norm{x_i}_2^2.
	$$
\end{lemma}
\begin{proof}
	Denote the eigenvalues of $I + \sum_{i=1}^n x_i x_i^{\top}$ by $1+\alpha_1,...,1+\alpha_d$ with $\alpha_j \geq 0$, $1\leq j\leq d$. Then
	\begin{align*}
	\det(I + \sum_{i=1}^n x_i x_i^{\top}) &= \prod_{j=1}^d (1 + \alpha_j)\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
	&=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
	&=1 + \sum_{i=1}^n \norm{x_i}_2^2.
	\end{align*}
\end{proof}

\begin{lemma}
	If $\lambda \geq C_\gamma$, it holds that
	$$
	\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\gamma^{2k-2}\norm{X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\log(\frac{\det(\bV_t)}{\det(\lambda I)}).
	$$
\end{lemma}
\begin{proof}
	\begin{align*}
	\det(\bV_t) &= \det(\bV_{t-1} + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}X_{t,\ba_k^{t}}X_{t, \ba_k^{t}}^{\top})\\
	&=\det(\bV_{t-1})\det(I + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}} (\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}})^{\top})\\
	&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
	&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
	\end{align*}
	Using the fact that $ 2\log(1+u) \geq u$ for any $u \in [0,1]$ and 
	$$
	0 \leq \norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma^{k-1}X_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma^{2k-2}/\lambda,
	$$
	we get
	\begin{align*}
	\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\norm{\gamma^{k-1}X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 &\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
	&\leq 2(\log(\det(\bV_t)) - \log(\det(\lambda I)))
	\end{align*}
\end{proof}

>>>>

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{X_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s): k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. By equation (\ref{eq:expectation}), we have $\EE[(\gamma_k'\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k' X_{s,\ba_k^s})$. By ridge regression of data 
$$
\{(\gamma_k' X_{s,\ba_k^s}, \gamma_k'\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]}
$$
where $\gamma_k' = \begin{cases}
\gamma_0, ~~k=1\\
\gamma_0-\gamma_k, ~~k\geq 2,
\end{cases}$
let $\hat{\theta}_t$ be the $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (X^{t,\top}X^{t} + \lambda I)^{-1} X^{t, \top} \bY^t
\end{equation}
where $X^t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k' X_{s,\ba_k^s}^{\top}$ and $\bY^t$ is the column vector whose elements are $\gamma_k' \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = X^{t,\top}X^{t} + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k'^2 X_{s,\ba_k^s}X_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.

\subsection{Algorithm}

@@

\section{Analysis}
Let
\begin{equation}
C_\gamma = \sum_{k=1}^{K} \gamma_k'^2.
\end{equation}

@@

\begin{lemma}
\label{lem:estimateTech}
Suppose $0 \leq p_1,...,p_K \leq 1$ and $u_1,...,u_K \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}$. Then
\begin{align*}
&~~f(K, w) \leq f(K, p) + \sum_{k=1}^{K} \gamma_k' u_k
\end{align*}
\end{lemma}
\begin{proof}
We prove this by induction. It holds obviously for $K=1$.
\begin{align*}
&~~f(K+1, w)\\
&= f(K, w) -\gamma_0 \prod_{k=1}^{K} w_k + \gamma_{K+1} (1 - w_{K+1}) \prod_{k=1}^{K} w_k\\
&~~ + \gamma_0 \prod_{k=1}^{K+1} w_k\\
&= f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - w_{K+1}) \prod_{k=1}^{K} w_k\\
&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - w_{K+1}) \prod_{k=1}^{K} p_k\\
&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - p_{K+1} - u_{K+1}) \prod_{k=1}^{K} p_k\\
&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - p_{K+1}) \prod_{k=1}^{K} p_k\\
&~~ + (\gamma_0 - \gamma_{K+1}) u_{K+1}\\
&\leq f(K+1, p) + \sum_{k=1}^{K+1} \gamma_k' u_k
\end{align*}
\end{proof}

@@

\begin{lemma}
Suppose $A = (a_1, ..., a_{\abs{A}})$. Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then we have the following properties.
\begin{itemize}
\item[(1)] $f(A, w) \leq \gamma_0 p_A + \gamma_{\abs{A}}$;
\item[(2)] $f(B_{k+1}, w) \leq f(B_k, w)$;
\item[(3)] $p_{B_{k+1}} \leq p_{B_k}$;
\item[(4)] $f(B_k, w) \leq \gamma_0 p_{B_{k+1}} + \gamma_{k+1}$.
\end{itemize}	
\end{lemma}

\begin{proof}
It suffices to prove these properties when $A = [m]$.
\begin{itemize}
\item[(1)]
$f(A, w) \leq \gamma_m(1 - p_A w_m) + \gamma_0 p_A w_m \leq \gamma_m + \gamma_0 p_A$

\item[(2)]
\begin{align*}
&f(B_k, w) - f(B_{k+1}, w)\\
&=\gamma_0 w_1 \cdots w_k - \gamma_{k+1} w_1 \cdots w_k (1 - w_{k+1})\\
&~~ - \gamma_0 w_1 \cdots w_{k} w_{k+1}\\
&=(\gamma_0 - \gamma_{k+1}) w_1 \cdots w_k (1 - w_{k+1}) \geq 0.
\end{align*}

\item[(3)]
Obvious.

\item[(4)]
$f(B_k, w) \leq \gamma_k (1 - p_{B_{k+1}}) + \gamma_0 p_{B_{k+1}}\leq \gamma_0 p_{B_{k+1}} + \gamma_{k}$
\end{itemize}
\end{proof}

\begin{proposition}
Suppose $A = (a_1, ..., a_{\abs{A}})$. Then there exists a prefix $B$ of $A$, such that 
$$
p_{B} \geq \frac{\frac{1}{2}f^* - \gamma_{B}}{\gamma_0}, \qquad \Delta_{B} \geq \frac{1}{2}\Delta_A.
$$ 
\end{proposition}
\begin{proof}
	Notice that $f^* \leq \gamma_0$. By above lemma, we have $[f(A,w), \gamma_0] \subset \bigcup [f(B_k,w), \gamma_0 p_{B_k} + \gamma_k]$.
\end{proof}

\begin{proposition}
Suppose $\gamma_K \leq \frac{1}{4} f_t^*$. With high probability $1-\delta$, 
$$
E[\Delta_{\bA_t}|\cH_t] \leq \frac{4}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proposition}
\begin{proof}
By above proposition, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\bB_t} \geq \frac{1}{4}\frac{f_t^*}{\gamma_0}$ and $\Delta_{\bB_t} \geq \frac{1}{2}\Delta_A$. Then we have
$$
\EE[\Delta_{\bA_t} | \cH_{t-1}] \leq \frac{4}{f_t^*} \EE[\Delta_{\bB_t} \bOne\{\Delta_{\bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
$$
Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t)$ and lemma \ref{lem:estimateU}, \ref{lem:increasing}, it holds that
$$
f(\bA_t^*, \theta_*^{\top}X_t) \leq f(\bB_t,\bU_t).
$$
Then by lemma \ref{lem:estimateTech}
$$
f(\bB_t,\bU_t) \leq f(\bB_t, \theta_*^{\top}X_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
\Delta_{\bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}

\begin{corollary}
With high probability $1-\delta$, 
$$
E[\Delta_{\bA_t}|\cH_t] \leq 4\sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}.
$$
\end{corollary}

\begin{theorem}
For any $\delta > 0$, with probability at least $1 - \delta$, we have
\begin{equation}
R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT})
\end{equation}
\end{theorem}
\begin{proof}
With probability at least $1-\delta$,
\begin{equation}
\begin{split}
&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{\bA_t}] \\
&\leq \sum_{t=1}^{T} 4 \sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}\\
&\leq 4\sqrt{\beta_T(\Delta)} \sum_{t=1}^{T} \sqrt{\bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}\\
&\leq 4\sqrt{\beta_T(\Delta)} \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
&\leq O(d^{3/4}\log(C_\gamma T)^{3/4}\sqrt{TK})
\end{split}
\end{equation}
\end{proof}

\begin{lemma} % det(V_t)
$\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
\end{lemma}
\begin{proof}
We have $\det(\bV_t) \leq (\trace(\bV_t)/d)^d$ and
\begin{align*}
&\trace(\bV_t)\\
& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \trace(X_{s,\ba_k^s} X_{s,\ba_k^s}^{\top})\\	
& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \norm{X_{s,\ba_k^s}}_2^2\\
& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k'^2=d\lambda + tC_\gamma.
\end{align*}
\end{proof}

\begin{lemma} % technical lemma for det
Let $x_i \in \RR^{d \times 1}, 1 \leq i \leq n$. Then we have
$$
\det(I + \sum_{i=1}^n x_i x_i^{\top}) \geq 1 + \sum_{i=1}^n \norm{x_i}_2^2.
$$
\end{lemma}
\begin{proof}
Denote the eigenvalues of $I + \sum_{i=1}^n x_i x_i^{\top}$ by $1+\alpha_1,...,1+\alpha_d$ with $\alpha_j \geq 0$, $1\leq j\leq d$. Then
\begin{align*}
&\det(I + \sum_{i=1}^n x_i x_i^{\top})\\
&= \prod_{j=1}^d (1 + \alpha_j)\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
&=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
&=1 + \sum_{i=1}^n \norm{x_i}_2^2.
\end{align*}
\end{proof}

\begin{lemma}
If $\lambda \geq C_\gamma$, it holds that
$$
\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\gamma^{2k-2}\norm{X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\log(\frac{\det(\bV_t)}{\det(\lambda I)}).
$$
\end{lemma}
\begin{proof}
\begin{align*}
&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}X_{t,\ba_k^{t}}X_{t, \ba_k^{t}}^{\top})\\
&=\det(\bV_{t-1})\\
&~~~~\det(I + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}} (\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}})^{\top})\\
&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
\end{align*}
Using the fact that $ 2\log(1+u) \geq u$ for any $u \in [0,1]$ and 
\begin{align*}
\norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 &\leq \norm{\gamma^{k-1}X_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1})\\
& \leq \gamma^{2k-2}/\lambda
\end{align*}
we get
\begin{align*}
&\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\norm{\gamma^{k-1}X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
&\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
&\leq 2(\log(\det(\bV_t)) - \log(\det(\lambda I)))
\end{align*}
\end{proof}
